\sysfull

### 2018-04-16 paper/evaluation.tex
removed todo from figures

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/memAccess}
	\caption{\sys memory access overhead breakdown; nc: no coalescing, sc: slow coalescing, ea: energy-aware coalescing. \todo{names of coalescing strategies in capitals; names of apps bold; reduce figure size by 40\%; Memory access over -> overhead breakdown}{Amjad}}
	\label{fig:coalmemory}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.49\columnwidth]{figures/page_exec-time}
	\includegraphics[width=0.49\columnwidth]{figures/pagePulls}
	\caption{\sys normalized runtime for various page sizes, \{32, 64,128,256\}\,bytes, per application (top) and respective page pulls (bottom)).\todo{add page numbers below for each bar for page faults; \# -> No. page faults; app names in bold; reduce Y size by 40\%; small space after 128 and 256 in top graph; white background}{Amjad}}
	\label{fig:page_size}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figures/memAccess}
	\caption{\sys memory access overhead breakdown; nc: no coalescing, sc: slow coalescing, ea: energy-aware coalescing.}
	\label{fig:coalmemory}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.49\columnwidth]{figures/page_exec-time}
	\includegraphics[width=0.49\columnwidth]{figures/pagePulls}
	\caption{\sys normalized runtime for various page sizes, \{32, 64,128,256\}\,bytes, per application (top) and respective page pulls (bottom).}
	\label{fig:page_size}
\end{figure}
